### 2017-07-12 README.Rmd
finish up CIs

>>>>

```
mtcars %>%
  specify(mpg ~ am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in means")
```

Two categorical variables (diff in proportions) (not yet implemented)

```
mtcars %>%
  specify(am ~ vs) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in prop")
```
